---
title: "FARS Interface"
author: "Will Russ"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package includes tools for loading, summarizing, and visualizing data from the Fatality Analysis Reporting System. 

We begin by loading FARS data for one year. We use the 'make_filename' function to get the filename for a specific year. Note that the working directly must be set to the folder containing the data.

```{r}
library(magrittr)
library(RPackageCoursera)
filename <- make_filename(2013)
filename
```

Now, we load the data using 'fars_read'.

```{r}
fars_data <- fars_read(filename)
head(fars_data)
```



We think there may be a rise in accidents in the winter months of 2015. We will use 'fars_summarize_years' to compare the number of accidents across years by month.

```{r}
fars_summarize_years(2013:2015)
```
We see there was a slight rise in 2015.



Finally, we want to visualize the accidents in 2015 for the state of South Carolina. We use 'fars_map_state' which draws a map of South Carolina with a dot for each accident.

```{r}
fars_map_state(45, 2015)
```


